### 2016-09-06 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to hose stream + gas burner reports
Updated event drawings + added callouts for open doorways in dimensioned drawings

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   181			  &		181			&		179		  \\
	~(3)~ Center burner on 				&   361			  &	   	361			&	   	360		  \\
	~(4)~ West double door opened 		&   418			  &    	416			&	   	415		  \\
	~(5)~ East double door opened 		&   538			  &    	536			&	   	535		  \\
	~(6)~ South exterior door opened 	&   604			  &    	597			&	   	597		  \\
	~(7)~ Center burner off				&   720			  &    	778			&	   	778		  \\
	~(8)~ Middle burner off				&   840			  &    	898			&	   	897		  \\
	~(9)~ Corner burner off				&   961			  &    	1018		&	   	1019	  \\
	(10) PPV fan on 					& 	1256		  &    	1316		&  	   	1319	  \\
	(11) PPV fan off 					& 	1892 		  & 	N/A 		& 		1380	  \\
	(12) PPV fan on 					& 	N/A 		  & 	N/A 		& 		1487 	  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2-4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}
\clearpage

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed a nearly identical procedure to change the ventilation. The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
	~(5)~ 2nd floor south exterior door closed	&   452			  	&    N/A		\\
	~(6)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
	~(7)~ PPV fan on 							&   624			  	&    594 		\\
	~(8)~ All burners off 						&   746 		  	&    721		\\
	~(9)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
	(10)  1st floor east double door opened		& 	N/A 			& 	 836		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage

>>>>

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lccc}
	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 	& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
	\midrule
	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
	~(2)~ Middle burner on 				&   181			  &		181			&		179		  \\
	~(3)~ Center burner on 				&   361			  &	   	361			&	   	360		  \\
	~(4)~ West double door opened 		&   418			  &    	416			&	   	415		  \\
	~(5)~ East double door opened 		&   538			  &    	536			&	   	535		  \\
	~(6)~ South exterior door opened 	&   604			  &    	597			&	   	597		  \\
	~(7)~ Center burner off				&   720			  &    	778			&	   	778		  \\
	~(8)~ Middle burner off				&   840			  &    	898			&	   	897		  \\
	~(9)~ Corner burner off				&   961			  &    	1018		&	   	1019	  \\
	(10) PPV fan on 					& 	1256		  &    	1316		&  	   	1319	  \\
	(11) PPV fan off 					& 	1892 		  & 	N/A 		& 		1380	  \\
	(12) PPV fan on 					& 	N/A 		  & 	N/A 		& 		1487 	  \\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
\end{minipage}
\caption{Tests~2--4 layout and event times.}
\label{fig:Tests_2-4_layout}
\end{figure}
\clearpage

@@

\subsection{Tests~22 \& 23}
Tests~22 and 23 followed a nearly identical procedure to change the ventilation. The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 22}	& \textbf{Test 23} \\
	\midrule
	~(1)~  All burners on 						&   0	  			&	 0			\\
	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
	~(7)~  PPV fan on 							&   652			  	&    612		\\
	~(8)~  PPV fan off              			&   798			  	&    761		\\
	~(9)~  All burners off 						&   829			  	&    794		\\
	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
	(11)   PPV fan on 	 						&   1065		  	&    940		\\
	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
\end{minipage}
\caption{Tests 22--23 layout and event times.}
\label{fig:west_test_22}
\end{figure}

@@

\begin{figure}[!ht]
\begin{minipage}[b]{0.8\columnwidth}
	\begin{flushleft}
	\begin{tabular}{lcc}
	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
	\toprule
	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
	\midrule
	~(1)~ All burners on 						&   0		  		&	 0			\\
	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
	~(5)~ 2nd floor south exterior door closed	&   452			  	&    N/A		\\
	~(6)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
	~(7)~ PPV fan on 							&   624			  	&    594 		\\
	~(8)~ All burners off 						&   746 		  	&    721		\\
	~(9)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
	(10)  1st floor east double door opened		& 	N/A 			& 	 836		\\
	\bottomrule
	\end{tabular}
	\end{flushleft}
\end{minipage}
\begin{minipage}[b]{0.9\columnwidth}
	\vspace{15pt}
	\centering
	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
\end{minipage}
\caption{Tests 24--25 layout and event times.}
\label{fig:west_test_24}
\end{figure}
\clearpage
